---
title: "Regression Models Course Project"
author: "Zanin Pavel"
date: "March 28, 2016"
output: pdf_document
---
[Link to project on GitHUB](https://github.com/Filareth2015/Regression-Models-Course-Project)     
[Link to project on RPub](https://github.com/Filareth2015/Regression-Models-Course-Project)

# Instruction

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:      
** "Is an automatic or manual transmission better for MPG"     
* "Quantify the MPG difference between automatic and manual transmissions"     

# Analysis

## Exploratory analysis


```{r , warning=FALSE, message = FALSE, echo=TRUE}
library (datasets)
data(mtcars)
head(mtcars)
```

```{r}
result <- t.test(mtcars$mpg ~ mtcars$am)
result$p.value
result$estimate
```  

```{r , warning=FALSE, message = FALSE, echo=TRUE}
mtcars$vs <- as.factor(mtcars$vs)
mtcars$am <- as.factor(mtcars$am)

boxplot(mpg ~ am, 
        data = mtcars, 
        ylab = "Miles Per Gallon", 
        xlab = "Transmission Type",
        main="Boxplot of MPG vs. Transmission",
        col = (c("pink","blue")))
```


## Simple linear regression model

```{r}
fit_simple <- lm(mpg ~ factor(am), data=mtcars)
summary(fit_simple)
```  

## Multivariable Regression Model

```{r}
data(mtcars)
fit_multi <- lm(mpg ~ . ,data=mtcars)
summary(fit_multi)
```

```{r}
fit_final <- lm(mpg ~ wt+hp+disp+cyl+am, data = mtcars)
par(mfrow = c(2, 2))
plot(fit_final)
```

